DraftOne

### 2016-07-08 DraftOne.Rmd

>>>>

Now a function for calc_t to use for seasonal binary exposure:

```{r}
bin_t <- function(n, p, trend = "no trend", amp = .3, custom_func = NULL, ...){
  day <- c(1:n)
  if (p > .5 & amp >1-p){
    stop(paste0("For p>.5, amp must be between 0 and 1-p."))
  }
  if (p < .5 & amp>p){
    stop(paste0("For p<.5, amp must be between 0 and p."))
  }
  if (trend == "cos1"){
    seasont <- p + amp * cos(2 * pi * (day / 365))
    } else if (trend == "cos2"){
    seasont <- p + amp/2 * cos(2 * pi * (day / 365)) +
      ifelse(day < 639 & day > 274, amp/2 * cos(2 * (pi * (day / 365))), 0)
    } else if (trend == "cos3"){
      seasont <- p + .75 ^ (day / 365) * amp * cos(2 * pi * (day / 365))
    } else if (trend == "linear"){
      seasont <- p+1/(day/n)
    } else if (trend == "curvilinear"){
      seasont <- p + day * (2 / n) + day^2 * (-1 / n^2)
    } else if (trend == "cos1linear"){
      seasont <- (p + (day / n)) * (p + amp * cos(2 * pi * (day / 365)))
    } else if (trend == "no trend"){
      seasont <- p
    } else if (trend == "custom" & !is.null(custom_func)) {
      arguments <- list(...)
      arguments$n <- n
      seasont <- do.call(custom_func, arguments)
    } else {
      stop(paste0("`trend` value is not a valid choice. Please check the",
                  " function documentation to select a valid option."))
    }
}
```
